\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Hyperlink settings
\hypersetup{
    colorlinks=true,        % Set to true to color links
    linkcolor=black,        % Color for internal links
    urlcolor=black,         % Color for URLs
    citecolor=black,        % Color for citations
    pdfborder={0 0 0},      % Remove border around links
    pdfpagemode=UseNone     % Do not show thumbnails on the left side
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
  \textbf{{\LARGE Shaifali Jain}} \\
  Email: \href{mailto:Shaifalijain.92@gmail.com}{Shaifalijain.92@gmail.com} \\
  Mobile: +91-6396121426 \\
  \href{https://github.com/Shaifali25}{Github: https://github.com/Shaifali25} \\
  \href{https://www.linkedin.com/in/shaifali-jain25/}{LinkedIn: https://www.linkedin.com/in/shaifali-jain25/} \\
\end{tabular*}





%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bhai Parmanand Institute DSEU}{Delhi, India}
      {Master in Computer applications - Information Technology;  GPA: 8.79}{July 2021 - June 2023}
      
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Javascript,HTML, CSS}
	\resumeSubItem{Frameworks}{~~~~React, nodejs}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, MySQL}
	
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Business Web Solutions}{Delhi}
    {Full Stack Development Intern}{Oct 2023 - Dec 2023}
    \resumeItemListStart
        \resumeItem{Web Application Development}
          {Developed and maintained web applications, collaborating with frontend and backend teams to ensure seamless user experience and optimized performance.}
        \resumeItem{Responsive UI }
          {Implemented responsive UI components using modern frameworks (e.g., React) and integrated RESTful APIs to facilitate data exchange between the client and server.}
    \resumeItemListEnd
    



\vspace{-1pt}
   \resumeSubheading
    {Admiral India EUI Ltd}{Remote}
    {QA Automation Intern}{Feb 2023 - Aug 2023}
    \resumeItemListStart
        \resumeItem{Automated Testing}
          {Developed and executed automated test scripts using tools like Selenium to ensure the reliability and performance of web applications.}
        \resumeItem{Collaboration and Issue Resolution}
          {Collaborated with development teams to identify and resolve software defects, improving overall code quality and reducing manual testing efforts.}
    \resumeItemListEnd


\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
    {TodoApp Project}{}
    {Technology Used: CSS, HTML, JavaScript, React}{}
    \resumeItemListStart
        \resumeItem{}
          {A project that allows users to add and view todos, and delete items as needed.}
        \resumeItem{}
          {Utilized React components, conditional programming, and props for dynamic functionality and parent-child communication.}
    \resumeItemListEnd

          
\vspace{-1pt}
   \resumeSubheading
    {Weather App Project}{}
    {Technology Used: CSS, HTML, JavaScript}{}
    \resumeItemListStart
        \resumeItem{}
          {A small project that fetches the weather report using an API request.}
        \resumeItem{}
          {Conditional programming concepts were used in this project.}
    \resumeItemListEnd

          \vspace{-1pt}
   \resumeSubheading
    {Automate Attendance  Portal Of Organization  (Admiral)}{}
    {Technology Used: Manual Testing, Java with Selenium, TestNg framework}{}
    \resumeItemListStart
        \resumeItem{}
          {Automate the portal's functionality by performing positive and negative cases using Java with Selenium.}
        \resumeItem{}
          {Used different types of Locators (X Path, CSS Selector, Id, ClassName, TagName, and many more).}
          \resumeItem{}
          {Along with this, use TestNg framework to generate the testing report. This framework is easy to group test cases and also understandable via annotations to make the program structured and user-friendly.}
          
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}



\vspace{-5pt}
%-----------Awards-----------------
\section{Certifications}
\begin{description}[font=$\bullet$]
\item {Automation Intern from Admiral - Aug, 2023}
\vspace{-5pt}
\item {Full-Stack Developer Intern - December, 2023 }
\vspace{-5pt}


\end{description}

\vspace{-5pt}

\section{Interests}
\begin{description}[font=$\bullet$]
\item {Avid Hodophile}
\vspace{-5pt}
\item {Musicophile }
\vspace{-5pt}
\item {Acquiring New Skills }


\end{description}

   



\end{document}
